Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-26 ms.tex
updated the amplifier offsets figure to show different migitation methods.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
{\it Bottom Panel:} The flux along the top row (without background subtraction) shows significant offsets due to pre-amp drifts and resets. These offsets are eliminated by reference pixel correction.
\textcolor{red}{Things to try: 1) put in a panel w/ background subtraction and maybe one with median of all ref pixels within an amplifier 2) check if there's any fringing 3) compare scatter in spectrum to photon + read noise}
}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
{\it First Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
{\it Second Panel:} Averaging all the reference pixels within an amplifier and subtracting the result reduces the offsets between amplifiers but there are still noticeable boundaries at X= 512, 1024 and 1536.
{\it Third Panel:} Reference pixel correction using the 4 non-illuminated pixels in each column significantly reduces offsets between amplifiers, but introduces read noise to each column.
{\it Fourth Panel:} Background subtraction with a linear fit along each column eliminates offsets between amplifiers without introducing any substantial new noise source.
\textcolor{red}{Things to try: 1) check if there's any fringing in the spectrum 2) compare scatter in spectrum to photon + read noise}
}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}
